---
title: "Address Term 2023"
author: "Soobin Choi"
date: "2023-05-01"
output: 
  github_document: 
    toc: TRUE
---

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo=TRUE, include=TRUE, comment="")
library(tidyverse)
library(dplyr)
library(ggplot2)
```

# Data Processing

```{r}
original <- read_csv("data/original_num.csv")
head(original)
```
```{r}
# process the column for the analysis - term, addressee gender, relationship
# And, change the name of columns

original1 <- original %>% 
  pivot_longer(`BRO-F-parent`:`MAN-F-stranger`, names_to = "TERM", values_to = "FREQUENCY") %>% 
  separate(col = TERM, c("TERM", "ADDR-GENDER", "RANK"), sep = "-") %>% 
  rename(`RESP-ID` = ResponseId,
         ATUSE = `AT ever use`,
         `RESP-GENDER` = GENDER) %>% 
  mutate(RANK = str_to_upper(RANK))
```

```{r}
# check the categories in AGE column
original1 %>% 
  select(AGE) %>% 
  unique()


original2 <- original1 %>% 
# remove NAs in AGE column
  filter(!is.na(AGE)) %>% 
  mutate(`RESP-GENDER` = str_to_title(`RESP-GENDER`)) %>%
  relocate(`ADDR-GENDER`, .after="RESP-GENDER") %>% 
  # merge '56-70' and 'over 70' into one category
  mutate_all(funs(str_replace_all(., "56-70", "Over 70"))) %>% 
  mutate_all(funs(str_replace_all(., "Over 70", "56-Over 70"))) %>% 
  # change 'other' gender to 'non-binary'
  map_dfr(~ str_replace_all(., "Other", "Non-Binary"))

```



```{r}
# make another column - clean up `SEXUALITY` column as binary value
org_clean <- original2 %>%
  mutate(SEXUALITY2 = grepl("(het|straight)", tolower(original2$SEXUALITY))) %>% 
  relocate(SEXUALITY2, .after = SEXUALITY) %>% 
  map_dfr(~ str_replace_all(., c("TRUE" = "Hetero", "FALSE" = "Non-Hetero"))) %>% 
  mutate(FREQUENCY = as.numeric(FREQUENCY))

```

Okay, I have left with 31,990 values in total.

# Address Term

## Analysis & Plots

### The usage of *dude* by gender and age

```{r}
# make new column called 'DUDE': TRUE means the participant uses *dude*, FALSE means they don't

dude_df <- org_clean %>% 
  mutate(DUDE = grepl("dude", org_clean$ATUSE))
head(dude_df, 10)

```

#### *Dude* by RESP-gender and age

```{r}
# Plot - Dude Usage by gender and age
dude_df %>% 
  group_by(`RESP-GENDER`, AGE, DUDE) %>% 
  summarise(Count = n_distinct(`RESP-ID`)) %>% 
  ggplot(aes(x = AGE, y = Count, fill = DUDE)) + 
  facet_wrap(vars(`RESP-GENDER`), ncol = 3) + 
  geom_col(position = "fill") +
  labs(title = "Dude Usage by Respondants' Gender and Age")
```


```{r}
'
dude_df %>% 
  filter(TERM == "DUDE" & `RESP-GENDER` != "Non-Binary") %>% 
  group_by(AGE, `ADDR-GENDER`, `RESP-GENDER`) %>% 
  summarise(count = n_distinct(`RESP-ID`)) %>% 
  unite(Gender, `RESP-GENDER`, `ADDR-GENDER`) %>% 
  ggplot(aes(x = AGE, weight = count, fill = Gender)) +
  geom_bar(position = "dodge")
'
```

#### *Dude* respondent's gender only

```{r}
# consider respondent's gender only - total count of people who answered that they use dude

dude_df %>% 
  group_by(`RESP-GENDER`, DUDE) %>% 
  summarise(Count = n_distinct(`RESP-ID`))

dude_df %>% 
  group_by(`RESP-GENDER`, DUDE) %>% 
  summarise(Count = n_distinct(`RESP-ID`)) %>% 
  ggplot(aes(x = `RESP-GENDER`, y = Count, fill = DUDE)) + 
  geom_col(position = "fill") + 
  ylab("Percentage") + 
  labs(title = "Dude Usage by Respondents' Gender")
```

#### *Dude* - Considering RESP & ADDR gender

```{r}

dude_df %>% 
  filter(TERM == "DUDE") %>% 
  filter(!is.na(FREQUENCY)) %>% 
  group_by(`ADDR-GENDER`, `RESP-GENDER`) %>% 
  summarise(mean_freq = mean(FREQUENCY)) %>% 
  ggplot(aes(x = `RESP-GENDER`, y = mean_freq, col = `ADDR-GENDER`, group = `ADDR-GENDER`))+
  geom_point() + 
  geom_text(aes(label = round(mean_freq, 2), vjust = -0.5, nudge_y = 0.1)) +
  geom_path() +
  labs(title = "Reported Frequency of Dude by Gender of Speaker and Addressee") +
  ylim(1.9, 2.65)


```


### Compare *dude* and *bro* by RESP & ADDR gender

```{r}
# sort people who use dude and/or bro

dudebro <- org_clean %>% 
  filter(grepl("dude", org_clean$ATUSE) == TRUE | grepl("bro", org_clean$ATUSE) == TRUE)
  

```


```{r}
# plot - dude/bro usage by rank and gender

dudebro %>% 
  filter(TERM %in% c("DUDE", "BRO")) %>% 
  group_by(`RESP-GENDER`, `ADDR-GENDER`, TERM, `RANK`) %>% 
  summarise(mean_freq = mean(as.numeric(FREQUENCY), na.rm = TRUE)) %>% 
  ggplot(aes(x = `RANK`, y = mean_freq,  group = TERM, col = TERM)) +
  facet_wrap(`ADDR-GENDER`~`RESP-GENDER`, ncol = 1, strip.position = "right", 
             labeller = labeller(
               `ADDR-GENDER` = c(`F`="Addr_F", `M`="Addr_M"),
               `RESP-GENDER` = c(`Feminine`="Resp_F", `Masculine`="Resp_M", `Non-Binary`="Non-Binary"))) + 
  geom_line() +
  geom_point() + 
  scale_y_continuous(limits = c(0, 4)) +
  labs(title = "Compare dude/bro based on interlocutors' gender", x = 'Relationship')

```

it contains too much information in one plot.
need to make it more reader-friendly

```{r}
# DUDE
dudebro %>% 
  filter(TERM == "DUDE") %>% 
  group_by(`RESP-GENDER`, `ADDR-GENDER`, TERM, `RANK`) %>% 
  summarise(mean_freq = mean(as.numeric(FREQUENCY), na.rm = TRUE)) %>% 
  unite(GENDER, `RESP-GENDER`, `ADDR-GENDER`)


dudebro %>% 
  filter(TERM == "DUDE") %>% 
  group_by(`RESP-GENDER`, `ADDR-GENDER`, TERM, `RANK`) %>% 
  summarise(mean_freq = mean(as.numeric(FREQUENCY), na.rm = TRUE)) %>% 
  unite(GENDER, `RESP-GENDER`, `ADDR-GENDER`) %>% 
  ggplot(aes(x = RANK, y = mean_freq, col = GENDER, group = GENDER)) +
  geom_point() +
  geom_line() + 
  xlab("Relationship") +
  labs(title = "Dude Usage by Gender") + 
  ylim(0.5, 4)

# BRO

dudebro %>% 
  filter(TERM == "BRO") %>% 
  group_by(`RESP-GENDER`, `ADDR-GENDER`, TERM, `RANK`) %>% 
  summarise(mean_freq = mean(as.numeric(FREQUENCY), na.rm = TRUE)) %>% 
  unite(GENDER, `RESP-GENDER`, `ADDR-GENDER`)


dudebro %>% 
  filter(TERM == "BRO") %>% 
  group_by(`RESP-GENDER`, `ADDR-GENDER`, TERM, `RANK`) %>% 
  summarise(mean_freq = mean(as.numeric(FREQUENCY), na.rm = TRUE)) %>% 
  unite(GENDER, `RESP-GENDER`, `ADDR-GENDER`) %>% 
  ggplot(aes(x = RANK, y = mean_freq, col = GENDER, group = GENDER)) +
  geom_point() +
  geom_line() +
  xlab("Relationship") +
  labs(title = "Bro Usage by Gender") + 
  ylim(0.5, 4)
```







### Is there any difference in the usage of *dude* by race?

```{r}
org_clean %>% 
  mutate(RACE = str_to_title(RACE)) %>% 
  group_by(RACE) %>% 
  summarize(n = n_distinct(`RESP-ID`))
```

# Sentence Rank

## Data Processing

```{r}
# load the data
rank_sent <- read_csv("data/rank_sent.csv")
head(rank_sent)


rank_clean <- rank_sent %>% 
  select(-Q23) %>% 
  rename(`RESP-ID` = ResponseId,
         ATUSE = `AT ever use`)
```


## Analysis

### Organize by question

#### MEETING

```{r}
colnames(rank_clean)

rank_clean %>% 
  select(contains(c("ID", "MUSIC")))
```


```{r}
meeting <- rank_clean %>% 
  select(contains(c("ID", "MEETING")))

meeting_final <- meeting %>% 
  rename_with(., ~gsub("MEETING-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  mutate(SENT = "Meeting", .after = TERM)

meeting %>% 
  rename_with(., ~gsub("MEETING-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  ggplot(aes(x = TERM, y = mean_rank)) +
  geom_path(group = 1, color = "dark green") +
  geom_point(color = "dark green") + 
  geom_text(aes(label = round(mean_rank, 2), hjust = -0.7, nudge_x = 0.1), color = "dark green") +
  scale_y_reverse(limits = c(5, 0.5)) +
  labs(title = "Mean Rank - \"When is the meeting?\"")
  
```

#### MUSIC

```{r}
music <- rank_clean %>% 
  select(contains(c("ID", "MUSIC")))

music_final <- music %>% 
  rename_with(., ~gsub("MUSIC-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  mutate(SENT = "Music", .after = TERM)
```


#### SHUTUP

```{r}
shutup <- rank_clean %>% 
  select(contains(c("ID", "SHUTUP")))

shutup_final <- shutup %>% 
  rename_with(., ~gsub("SHUTUP-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  mutate(SENT = "Shut up", .after = TERM)
```

#### GOODTOSEE

```{r}
goodtosee <- rank_clean %>% 
  select(contains(c("ID", "GOODTOSEE")))

goodtosee_final <- goodtosee %>% 
  rename_with(., ~gsub("GOODTOSEE-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  mutate(SENT = "Good to see", .after = TERM)
```

#### SIGNAL

```{r}
signal <- rank_clean %>% 
  select(contains(c("ID", "SIGNAL")))


signal_final <- signal %>% 
  rename_with(., ~gsub("SIGNAL-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  mutate(SENT = "Signal", .after = TERM)
```


#### EMAIL

```{r}
email <- rank_clean %>% 
  select(contains(c("ID", "EMAIL")))


email_final <- email %>% 
  rename_with(., ~gsub("EMAIL-", "", .x)) %>% 
  pivot_longer(!`RESP-ID`, names_to = "TERM", values_to = "RANK") %>% 
  na.omit(RANK) %>% 
  group_by(TERM) %>% 
  summarise(mean_rank = mean(RANK)) %>% 
  mutate(SENT = "Email", .after = TERM)
```

#### Combine all the results

```{r}
sent_final <- rbind(meeting_final, music_final, goodtosee_final, shutup_final, signal_final, email_final)

sent_final %>% 
  group_by(TERM) %>% 
  summarize(mean = mean(mean_rank))

sent_final %>% 
  ggplot(aes(x = TERM, y = mean_rank, group = SENT, col = SENT)) +
  geom_path() +
  geom_point() + 
  scale_y_reverse(limits = c(4, 1))
  scale_x_discrete(limits = c("DUDE", "BRO", "BRUH", "GIRL"))

```



# *Bro* vs. *Bruh* - Difference

## Data Processing 

```{r}
library(tidytext)
library(stopwords)
brobruh <- read_csv("data/brobruh.csv")
head(brobruh)
```

```{r}
# tokenize the response by sentence, sort out the columns we don't need
brobruh2 <- brobruh %>% 
  rename(ANSWER = Q23) %>% 
  select(-c(`GENDER-4-TEXT`, `AT ever use`)) %>% 
  unnest_tokens(`SENT-TOK`, ANSWER, token = "sentences") %>% 
# need to split the sents by comma, too.
  unnest_tokens(`SENT-TOK2`, `SENT-TOK`, token = stringr::str_split, pattern = ",") %>% 
  na.omit(`SENT-TOK`)


```


```{r}
brobruh_clean <- brobruh2 %>% 
  mutate(BRO = grepl('bro', `SENT-TOK2`),
         BRUH = grepl("bruh", `SENT-TOK2`)) %>% 
  relocate(BRO, BRUH, .before = `SENT-TOK2`)

bro_clean <- brobruh_clean %>% 
  filter(BRO == TRUE & BRUH == FALSE)

bruh_clean <- brobruh_clean %>% 
  filter(BRO == FALSE & BRUH == TRUE)


head(bro_clean)
head(bruh_clean)
```

## Analysis?

```{r}
# load up stopwords
snowball <- stopwords(language = "en", source = "snowball", simplify = TRUE)
nltk <- stopwords(language = "en", source = "nltk", simplify = TRUE)
smart <- stopwords(language = "en", source = "smart", simplify = TRUE)

# clean up -- sents containing 'bro'
bro_final <- bro_clean %>% 
  unnest_tokens(TOKEN, `SENT-TOK2`) %>%
  filter(!(TOKEN %in% snowball | TOKEN %in% nltk | TOKEN %in% smart | 
           TOKEN %in% c("bro", "bros", "bruh", "don’t", 'i’m', 'it’s',
                        'people', "person", 'term', "address", "expression", "feel", "feels")))


# clean up -- sents containing 'bruh'
bruh_final <- bruh_clean %>% 
  unnest_tokens(TOKEN, `SENT-TOK2`) %>% 
  filter(!(TOKEN %in% snowball | TOKEN %in% nltk | TOKEN %in% smart | 
           TOKEN %in% c("bro", "bros", "bruh", "don’t", 'i’m', 'it’s',
                        'people', "person", 'term', "address", "expression", "feel", "feels")))
```

### Plot

```{r}
# `bro` plot
bro_final %>% 
  count(TOKEN, sort = TRUE, name = "Count") %>% 
  mutate(TOKEN = reorder(TOKEN, Count)) %>% 
  head(20) %>% 
  ggplot(aes(x = Count, y = TOKEN)) +
  geom_col() + 
  labs(title = "Top 20 Tokens Used to Describe 'Bro'")
```

```{r}
#`bruh` plot
bruh_final %>% 
  count(TOKEN, sort = TRUE, name = "Count") %>% 
  mutate(TOKEN = reorder(TOKEN, Count)) %>% 
  head(20) %>% 
  ggplot(aes(x = Count, y = TOKEN)) +
  geom_col() + 
  labs(title = "Top 20 Tokens Used to Describe 'Bruh'")
```








